---
title: "Factors that affects House price in USA"
author: "Yuxuan Wang"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---

# Project description

The real estate markets, present an interesting opportunity for data analysts to analyze and predict where property prices are moving towards. Prediction of property prices is becoming increasingly crucial, offering valuable insights into both the broader market's trajectory and the economic health of a nation. This project tackles the classic problem of house price prediction using machine learning and statistical methods, with a specific focus on identifying the key factors influencing housing prices in the United States. Furthermore, we dive into a case study of Seattle, comparing the city's housing market dynamics to those of the broader national market, and provides a more comprehensive understanding of the factors affecting property prices at both local and national levels.

This is the pdf link of the final report.[View PDF](JSC370 Final.pdf)


```{r message=FALSE, echo=FALSE, warning=FALSE}
library(httr)
library(tidyverse)
library(plotly)
library(widgetframe)
library(tidytext)
library(dplyr)
library(kableExtra)

library(rpart)
library(rpart.plot)
library(randomForest)
library(gbm)
library(xgboost)
library(caret)

```



## Showcasing plots {.tabset}
### Figure 1
This figure shows the age and condition distribution in different city. It can reflects the housing condition for each city, and we can see the city's culture and economy behind the house age and condition.
```{r echo=FALSE, message=FALSE,warning=FALSE}
# data <- read.csv("data.csv", header=TRUE)
data <- read.csv("https://raw.githubusercontent.com/Ekconick/my-website/main/data/data.csv", header=TRUE)
# seattle <- read.csv("train.csv", header=TRUE)
seattle <- read.csv("https://raw.githubusercontent.com/Ekconick/my-website/main/data/train.csv", header=TRUE)

data<- na.omit(data)
data$waterfront <- factor(data$waterfront, levels = c(0, 1), labels = c("No", "Yes"))

data$view <- factor(data$view, levels = c(0, 1, 2, 3, 4), ordered = TRUE)

data$condition <- factor(data$condition, levels = c(1, 2, 3, 4, 5), ordered = TRUE)

data$age <- 2014 - data$yr_built
data <- data[, c("price", "bedrooms", "bathrooms", "sqft_living", "sqft_lot", 
                 "sqft_above", "floors", "waterfront", 
                 "view", "condition", "age","city")]

seattle <- na.omit(seattle)

data_seattle <- filter(data, city == "Seattle")

data_seattle <- data_seattle[, c("price","bedrooms", "bathrooms", "sqft_above", "sqft_lot")]

seattle_renamed <- seattle %>%
  rename(bedrooms = beds, 
         bathrooms = baths, 
         sqft_above = size, 
         sqft_lot = lot_size)
seattle_renamed<- seattle_renamed[, c("price","bedrooms", "bathrooms", "sqft_above", "sqft_lot")]

new_seattle <- bind_rows(data_seattle, seattle_renamed)
p3 <- ggplot(data, aes(x=condition, y=age, color=city))+
  geom_point(alpha = 0.5)
ggplotly(p3)
```


### Figure 2
We can see though the relationship between the number of bathrooms, house price, and house age, this is a scatter plot with coloring based on age.
```{r echo=FALSE, message=FALSE,warning=FALSE}
p4 <- ggplot(data, aes(x = bathrooms, y = price, color = as.factor(age))) +
  geom_point(alpha = 0.5) + 
  labs(title = "Relationship Between Bathrooms and Price by House Age",
       x = "Number of Bathrooms",
       y = "House Price",
       color = "House Age")

# Convert to an interactive plotly graph
ggplotly(p4)
```
### Figure 3
This heatmap illustrates the relationship and distribution between the number of bathrooms and bedrooms in houses across different floor levels.
```{r echo=FALSE, message=FALSE,warning=FALSE}
data_summary <- data %>%
  group_by(bathrooms, bedrooms, floors) %>%
  summarize(count = n(), .groups = 'drop')

p5 <- ggplot(data_summary, aes(x = bathrooms, y = bedrooms, fill = count)) +
  geom_tile() +
  scale_fill_gradient(low = "blue", high = "red") +
  labs(title = "Heatmap of House Characteristics", x = "Number of Bathrooms", y = "Number of Bedrooms") +
  facet_wrap(~floors)

ggplotly(p5)
```






{-}

